foreground detection via Deep Variation Transformation

### 2018-08-22 draft.tex
.

%GMM 
% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are .... to be if there exists ....， 我也是在其他论文里借过来用的。原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time. Pixels are considered to be background if there exists a Gaussian includes their values with sufficient evidence. 
%GMM+
% Ren: 这里你说看不懂，我的意思是想说，GMM+里面参数会自动更新。并且每一个像素位置的高斯个数也会自适应调整。原文里说的是： Recursive equations are used to constantly update the parameters and but also to simultaneously select the appropriate number of components for each pixel.
An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, which can automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
%codebook
%Another popular algorithm in pixel based category is based on the Codebook. 
%Ren: 干脆删掉这一句了。。。
%Ren: 下面也重新写了。
Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.  
Then incoming pixels are compared with those of the codewords, to see if their distances lies within a certain bound. 
%KDE
% Ren这里确实没写好，因为有点看不太明白KDE.
A non-parametric background model is proposed in \cite{Elgammal2000Non}. Authors assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
%Vibe
% Ren: 关于这个Another我觉得没问题啊，因为之前一句是讲非参数的方法KDE,这里说另一个非参数的方法我觉得没毛病啊。
% Ren: 还有 when there exists 这个短语确实没毛病啊，搜谷歌学术里这么用的也很多啊。
Another non-parametric method is proposed by Barnich\cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). The background model of ViBe consists of pixel samples from the video stream. Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists at least K samples with a distance to itself within a certain range R. 
%PBAS
%
% 这里上下两句话里，我用了一个R，一个R(X)，这两个东西是有关系的，ViBe里面要看距离是不是小于R, 下面这个论文是看距离是不是小于R(X),也就是说每个像素点位置，这个R是不一样的。
%
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.

%提出其他方法的问题，指出他们的缺陷
However, Those assumptions of pixels' independence are incorrect or inapplicable to many real-world scenes. 
There is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
In most cases, pixels-based methods are only concerned with pixels distribution, and ignore the order information of input frames by default.
%提出我们的改进,我们认为像素在时序上是互相依赖的
To address this shortcoming, we introduce a novel framework of variation transformation learing, which assumpt that there is a tight interdependence in pixel's historical observations.
%所以我们把像素整合到一起
In this case, pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
%这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
The benefit of bringing together the observations is to ensure the data integrity and preserve the temporal coherence of our training data. And that guarantee us the ability to take advantage of the temporal coherence. 
%所以我们方法比基于像素的要好。
Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
\subsection{region-based approach}
Region-based approaches assume that the neighboring pixels have a similar variation as the pixel itself. Hence the spatial correlation is taken into consideration to refine the pixel-level classification.

%(Regularized region-based)
A region-based MoG is proposed by Varadarajan et al.\cite{2015_PR_Varadarajan20153488} Their model are derived from expectation maximization theory, which takes into consideration neighboring pixels while generating the model of the observed scene.
% Spatiotemporal GMM
Another GMM based method named Spatiotemporal GMM algorithm was proposed in \cite{2017_TPAMI_GANGWANG}. the authors combine the GMM with constrains of temporal and spatial information from the optical flow and superpixels.
%(Bayesian Modeling)
In \cite{Sheikh2005Bayesian}, Sheikh et al. introduce a MAP-MRF framework, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
%(Robust Foreground Object ICPR2010 Vikas Reddy )
In \cite{Reddy2010Robust}, given frames are divided into overlapping blocks. Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure, and a temporal correlation check.
%( Robust Region-Based ICPR)
Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color. Any foreground region that does not exist in map1 could be recovered from map2.

>>>>

%GMM 
% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are .... to be if there exists ....， 我也是在其他论文里借过来用的。原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time. Pixels are considered to be background if there exists a Gaussian includes their values with sufficient evidence. 
%GMM+
% Ren: 这里你说看不懂，我的意思是想说，GMM+里面参数会自动更新。并且每一个像素位置的高斯个数也会自适应调整。原文里说的是： Recursive equations are used to constantly update the parameters and but also to simultaneously select the appropriate number of components for each pixel.
An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, which can automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
%codebook
%Another popular algorithm in pixel based category is based on the Codebook. 
%Ren: 干脆删掉这一句了。。。
%Ren: 下面也重新写了。
Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.  
Then incoming pixels are compared with those of the codewords, to see if their distances lies within a certain bound. 
%KDE
% Ren这里确实没写好，因为有点看不太明白KDE.
A non-parametric background model is proposed in \cite{Elgammal2000Non}. Authors assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
%Vibe
% Ren: 关于这个Another我觉得没问题啊，因为之前一句是讲非参数的方法KDE,这里说另一个非参数的方法我觉得没毛病啊。
% Ren: 还有 when there exists 这个短语确实没毛病啊，搜谷歌学术里这么用的也很多啊。
Another non-parametric method is proposed by Barnich\cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). The background model of ViBe consists of pixel samples from the video stream. Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists at least K samples with a distance to itself within a certain range R. 
%PBAS
%
% Ren :这里上下两句话里，我用了一个R，一个R(X)，这两个东西是有关系的，ViBe里面要看距离是不是小于R, 下面这个论文是看距离是不是小于R(X),也就是说每个像素点位置，这个R是不一样的。
%
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.

%提出其他方法的问题，指出他们的缺陷
However, The assumption that pixels are independent to their spatical neighbors is untenable in practice. 
% Ren: 下面这一段，你说不知所云，我的意思是，之前的方法大多只考虑了像素值分布的概率，而不管它们变化过程中的顺序性。
On the other hand, most pixels-based methods are only concerned with pixels distribution, and ignore the order information of input frames by default.
But there is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
%提出我们的改进,我们认为像素在时序上是互相依赖的
% tight interdependence 明明在google scholar里查得到很多用的好不好...
To address this shortcoming, we introduce a novel framework of variation transformation learing, which assume that there is a tight interdependence in pixel's historical observations.
%所以我们把像素整合到一起
% In this case在google scholar里也查得到很多啊
In this case, pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
%这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
The benefit of bringing together the observations is to ensure the data integrity and preserve the temporal coherence of our training data. And that guarantee us the ability to take advantage of the temporal coherence. 
%所以我们方法比基于像素的要好。
Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
%
%
%
%
%
%
\subsection{region-based approach}
% Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
Region-based approaches assume that the neighboring pixels have similar intensities. Hence the spatial correlation is taken into consideration to refine the pixel-level classification.

%(Regularized region-based)
A region-based MoG is proposed by Varadarajan et al.\cite{2015_PR_Varadarajan20153488}. Their model are derived from expectation maximization theory, which takes into consideration neighboring pixels while generating the model of the observed scene.
% Spatiotemporal GMM
Another GMM based method named Spatiotemporal GMM algorithm was proposed in \cite{2017_TPAMI_GANGWANG}. the authors combine the GMM with constrains of temporal and spatial information from the optical flow and superpixels.
%(Bayesian Modeling)
In \cite{Sheikh2005Bayesian}, Sheikh et al. introduce a MAP-MRF framework, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
%(Robust Foreground Object ICPR2010 Vikas Reddy )
In \cite{Reddy2010Robust}, given frames are divided into overlapping blocks. Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure, and a temporal correlation check.
%( Robust Region-Based ICPR)
Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color. Any foreground region that does not exist in map1 could be recovered from map2.
